Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-07-25 pirouette_article.tex
Changes @rsetienne

# Create phylogeny
phylogeny <- create_exemplary_dd_tree(
  n_taxa = 6, 
  crown_age = 10,
  extinction_rate = 0.1
)

# Use standard pirouette setup
pir_params <- create_std_pir_params()

# Create the inference model for the generative model explicitly
pir_params$experiments[[1]]$inference_model$tree_prior <- create_yule_tree_prior()
pir_params$experiments[[1]]$inference_model$site_model <- create_jc69_site_model()
pir_params$experiments[[1]]$inference_model$clock_model <- create_strict_clock_model()

# Simulate a twin tree using BD explicitly
pir_params$twinning_params$sim_twin_tree_fun <- get_sim_bd_twin_tree_fun()

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_30/errors.png}
  \caption{
    \new{The inference error made 
    when using the generative substitution and clock models (in this case JC69 and strict clock) and a Yule tree prior (this is the assumed generative model because the real generative model is of course unknown) and when using the best-fitting candidate model (in this case JC69, relaxed log-normal and BD), for both the true tree generated by the novel diversification model and for the twin tree.
    The twin distributions show the baseline inference error.}
    Vertical dashed lines show the median error value per distribution.
  }
  \label{fig:example_30}
\end{figure}

>>>>

# Create a DD phylogeny with 6 taxa and a crown age of 10
phylogeny <- create_exemplary_dd_tree()

# Use standard pirouette setup. This creates a list object with all settings for generating the alignment, the inference using BEAST2,  the twinning parameters to generate the twin tree and infer it using BEAST2, and the error measure  
pir_params <- create_std_pir_params()

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_30/errors.png}
  \caption{
    \new{The impact of the tree prior for the example tree in Figure 2. The alignment for this true tree was generated using a JC69 substitution model and strict clock model. For inferring the tree from this alignment in the 'generative' scenario the same substitution and clock models were used, and a Yule tree prior (this is the assumed generative model because the real generative model is of course unknown). In the 'best' scenario the best-fitting candidate models (JC69 substitution model, relaxed log-normal clock model and BD tree prior) were used. For the twin tree, the same models were chosen, except that BD was used to generate and infer the twin tree in the 'generative' scenario.
    The twin distributions show the baseline inference error.}
    Vertical dashed lines show the median error value per distribution.
  }
  \label{fig:example_30}
\end{figure}

### 2020-07-25 pirouette_supplement.tex
Changes @rsetienne

Until it is on CRAN, and for the most up-to-date version, 
one can download and install the package from \verb;pirouette;'s GitHub 
repository. We do first need the \verb;mcbette; and \verb;nodeSub; packages:
\begin{lstlisting}[
    language = R,
    floatplacement = ht,
    frame = single
]
remotes::install_github(
  "richelbilderbeek/mcbette"
)
remotes::install_github(
  "thijsjanzen/nodeSub"
)
\end{lstlisting}

>>>>

Until it is on CRAN, and for the most up-to-date version, 
one can download and install the package from \verb;pirouette;'s GitHub 
repository. We first need the \verb;mcbette;, \verb;tiebeaur; and \verb;nodeSub; packages:
\begin{lstlisting}[
    language = R,
    floatplacement = ht,
    frame = single
]
remotes::install_github(
  "richelbilderbeek/mcbette"
)
remotes::install_github(
  "richelbilderbeek/tiebeaur"
)
remotes::install_github(
  "thijsjanzen/nodeSub"
)
\end{lstlisting}
